On Secure Delegation of SampBQP with a Classical Client

### 2020-04-04 qpip.tex
Change notation for trace distance

	Now suppose $p_j\geq\frac{1}{2}-2\kappa$.
	By \Cref{cor:HamCheck} we have a lower bound for the fidelity between $\rho_j$ and $\psi_{C'(x)}$:
	$$p_j>\frac{1}{2}-2\kappa\Rightarrow F(\rho_j, \psi_{C'(x)})\geq1-\varepsilon^2.$$
	which in turn implies a lower bound on the respective trace distance:
	$$T(\rho_j, \ket{\psi_{C'(x)}})<\varepsilon.$$
	\Ethan{Trace distance notation}

>>>>

	Now suppose $p_j\geq\frac{1}{2}-2\kappa$.
	By \Cref{cor:HamCheck} we have a lower bound for the fidelity between $\rho_j$ and $\psi_{C'(x)}$:
	$$p_j>\frac{1}{2}-2\kappa\Rightarrow F(\rho_j, \psi_{C'(x)})\geq1-\varepsilon^2.$$
	which in turn implies a lower bound on the respective trace distance:
	$$\frac{1}{2}\norm{\rho_j - \ket{\psi_{C'(x)}}}_1<\varepsilon.$$
	\Ethan{Trace distance notation}
